---
title: "Chapter7 exercise"
author: "houdongdong\\
        15420141151964"

output: 
  pdf_document: 
    latex_engine: xelatex
---
##7.1
let $y_i$ denote the number of people deaths from leukemia among $n_i$ people with \emph{i}th covariate pattern. The dose is difined by the lower end of each dose interval


```{r}
y<-c(13,5,5,3,4,18)
n<-c(391,205,156,50,35,51)
n_y<-n-y
death.mat<-cbind(y,n_y)
x<-c(0,1,10,50,100,200)
```
We choose the logisitic regression model to fit the data
$$log\frac{\pi_i}{1-\pi_i}=\beta_0+\beta x; \quad y_i\sim Bin(n_i,\pi_i)$$
the fitted results are as follows:
```{r}
res.glm<-glm(death.mat~x,family=binomial(link="logit"))
summary(res.glm)
```

we can make a comparation between the observed value and fitted value
```{r}
fit<-res.glm$fitted #estimated proportion of death from leukemia
yfit<-n*fit
rbind(y,fit,yfit)
```

According to the residual deviance and the fitted value, we can make the conclusion that the model fit the data well.

The estimated proportion of death from leukemia and etsimated coefficient indicate that higher radiation dose increses the death rate from leukemia.


##7.2
(a) if $\beta_1=\beta_2$, then $\pi_1=\pi_2$, it's obviously that $\phi=1$

(b) \begin{eqnarray*}
log\phi_j &=& log O_{1j}-log O_{2j}\\
&=&log\frac{\pi_{1j}}{1-\pi_{1j}}-log\frac{\pi_{2j}}{1-\pi_{2j}}\\
&=& \alpha_1+\beta_1 x_j -(\alpha_2+\beta_2 x_j)\\
&=& \alpha_1-\alpha_2+x_j(\beta_1-\beta_2)\\
\end{eqnarray*}
if $\beta_1= \beta_2$, we have $log\phi_j=\alpha_1-\alpha_2$, which is constant for all \emph{j}.





























